|

### 2022-02-28 paper/dcpo_demsupport.Rmd
rmd updated for replication

p_install(janitor, force = FALSE)
p_install_gh(c("fsolt/DCPOtools"), force = FALSE)

# load all the packages you will use below
p_load(
    # data
    dataverse,

    # analysis
    plm,

@@

Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")

@@

```{r compare_n}
if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
  dataverse::get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>%
    read_csv(col_types = "cdcddcdc") %>%
    write_csv("data/supdem raw survey marginals.tab")
}

@@

```{r pointAJPS}
if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
  get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
    read_csv(col_types = "cdcddcdc") %>%
    write_csv(here("data", "Support_democracy_ajps.csv"))
}

@@

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier
if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
  get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
    save(file = here("data", "dem_mood_apsr.RData"))
}

>>>>

if(!require(janitor)) p_install(janitor, force = FALSE)
if(!require(gesisdata)) remotes::install_github("fsolt/gesisdata") # dependent package for DCPOtools
if(!require(DCPOtools)) remotes::install_github("fsolt/DCPOtools")

# load all the packages you will use below
p_load(
    # data
    # dataverse,

    # analysis
    plm,
    DCPOtools,

@@

Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
# Sys.setenv("DATAVERSE_KEY" = "your_keys") # replace your_keys with true API keys

@@

```{r compare_n}
# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
# if (!file.exists(here("data", "supdem raw survey marginals.tab"))) {
#   dataverse::get_file("supdem raw survey marginals.tab", "10.7910/DVN/HWLW0J") %>%
#     read_csv(col_types = "cdcddcdc") %>%
#     write_csv("data/supdem raw survey marginals.tab")
# }

@@

```{r pointAJPS}
# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
# if (!file.exists(here("data", "Support_democracy_ajps.csv"))) {
#   get_file_by_doi(filedoi = "10.7910/DVN/HWLW0J/MVXNFC") %>%
#     read_csv(col_types = "cdcddcdc") %>%
#     write_csv(here("data", "Support_democracy_ajps.csv"))
# }

@@

```{r pointAPSR}
# Reusing the sd.plm object, thus input data here rather than earlier
# One can download the original data of the AJPS paper with the following codes AFTER set Sys.setenv("DATAVERSE_KEY" = "your_keys")
# if (!file.exists(here("data", "dem_mood_apsr.RData"))) {
#   get_dataframe_by_doi(filedoi = "10.7910/DVN/FECIO3/ACMGQG") %>%
#     save(file = here("data", "dem_mood_apsr.RData"))
# }
